Gaia's constraints on the extremely massive ($\sim$$150\,M_\odot$) runaway star candidate VFTS682

### 2018-06-10 VFTS682_APJL.tex
table-inconsistencies removed

    %  &RA &[degree] &  \phantom{-}84.73 % $\pm$  0.03
   %                     & \multirow{2}{*}{\cite{evans:11}}\\[5pt]
    %  &DEC & [degree] & -69.07 % $\pm$  0.05
     %                   & \\[5pt]
      \multicolumn{5}{l}{\emph{Gaia's relative proper motion for VFTS 682 }} \\                 
      &$\delta\mu_\mathrm{RA}$  &[$\masyr$] & 0.10$\pm$0.07 & (1,4) \\
      &$\delta\mu_\mathrm{DEC}$  &[$\masyr$] & 0.08$\pm$0.09 &  (1,4) \\
      &$\delta\mu_\mathrm{}$  &[$\masyr$] & \SdM{xxx}$\pm$\SdM{xxx} &  (1,4) \\
                 &$v_\mathrm{2d}$  &[$\kms$] & \SdM{xxx}$\pm$\SdM{xxx} & (1,4)\\  
 \hline     
          \multicolumn{5}{l}{\emph{HST's independent determination of the relative proper motion for VFTS 682}} \\  
      &$\delta\mu_\mathrm{RA, HST}$  &[$\masyr$] & 0.01$\pm$0.13 & (3) \\
      &$\delta\mu_\mathrm{DEC, HST}$  &[$\masyr$] & 0.2$\pm$0.1 &  (3) \\
       &$\delta\mu_\mathrm{HST}$  &[$\masyr$] & 0.20$\pm$0.15 &  (3) \\
                  &$v_\mathrm{2d, HST}$  &[$\kms$] & \SdM{$47\pm24$}\footnote{\SdM{This can't be right, the error bar is suddenly smaller than in the mas units!}} & (3)\\  
\hline
      \multicolumn{5}{l}{\emph{ Direction and magnitude w.r.t the vector pointing away from R136}} \\     
       &$\theta^{*}$  &[degrees] &  \SdM{xxx}$\pm$\SdM{xxx}  & (1,4)\\  
        &$v_\mathrm{2d, \parallel}$  &[$\kms$] & \SdM{xxx}$\pm$\SdM{xxx} & (1,4)\\  
 %          &$v_\mathrm{2d}$  &[$\kms$] & \SdM{xxx}$\pm$\SdM{xxx} & (1,4)\\

@@

We list their data in \Tabref{tab:vfts682}.  The errorbars are larger than we obtain from \emph{Gaia}, but the values are consistent. \SdM{Actually they are not consistent with values found in one of Danny's emails. What is going on here?}

>>>>

    %  &RA &[degree] &  \phantom{-}84.73 % $\pm$  0.03
   %                     & \multirow{2}{*}{\cite{evans:11}}\\[5pt]
    %  &DEC & [degree] & -69.07 % $\pm$  0.05
     %                   & \\[5pt]
      \multicolumn{5}{l}{\emph{Gaia's relative proper motion for VFTS 682 }} \\                 
      &$\delta\mu_\mathrm{RA}$  &[$\masyr$] & 0.103$\pm$0.080 & (1,4) \\
      &$\delta\mu_\mathrm{DEC}$  &[$\masyr$] & 0.086$\pm$0.100 &  (1,4) \\
      &$\delta\mu_\mathrm{}$  &[$\masyr$] & \SdM{0.13}$\pm$\SdM{0.09} &  (1,4) \\
                 &$v_\mathrm{2d}$  &[$\kms$] & \SdM{32}$\pm$\SdM{21} & (1,4)\\  
 \hline     
          \multicolumn{5}{l}{\emph{HST's independent determination of the relative proper motion for VFTS 682}} \\  
      &$\delta\mu_\mathrm{RA, HST}$  &[$\masyr$] & 0.01$\pm$0.13 & (3) \\
      &$\delta\mu_\mathrm{DEC, HST}$  &[$\masyr$] & 0.20$\pm$0.10 &  (3) \\
       &$\delta\mu_\mathrm{HST}$  &[$\masyr$] & 0.20$\pm$0.10 &  (3) \\
                  &$v_\mathrm{2d, HST}$  &[$\kms$] & \SdM{$47\pm24$} & (3)\\  
\hline
      \multicolumn{5}{l}{\emph{ Direction and magnitude w.r.t the vector pointing away from R136}} \\     
       &$\theta^{*}$  &[degrees] &  \SdM{xxx}$\pm$\SdM{xxx}  & (1,4)\\  
        &$v_\mathrm{2d, \parallel}$  &[$\kms$] & \SdM{xxx}$\pm$\SdM{xxx} & (1,4)\\  
 %          &$v_\mathrm{2d}$  &[$\kms$] & \SdM{xxx}$\pm$\SdM{xxx} & (1,4)\\

@@

We list their data in \Tabref{tab:vfts682}.  The errorbars are comparable with those we obtain from \emph{Gaia}.  However the direction and angle are different.  
\SdM{Can we please get theta Gaia and theta HST in the table.}
